\plaintitle

### 2016-09-20 drafts/labor/relationships.tex
wrapping this up to take to gates

\subsubsubsection{\crowdworkpers}
\topic{The relationships of workers with their work, with their peers, and with others
are complex and not especially well--understood.}
Researchers have begun to appreciate
the sociality of crowd workers in labor markets
\cite{crowdcollab}.
Still, the study of these communities is made more challenging by
the limited access to workers on these sites of work
inherent to digital spaces made without social affordances
\cite{miller2011understanding}.
% Nevertheless, a number of interesting findings have
% already emerged in the crowd work literature%
% , which we can report here.
We can break this general body of work into the three groups we named earlier:
workers' relationships
\begin{inlinelist}
% \item with \textit{work}, % \nameref{ch:workRelationship},
\item with \textit{requesters}, and
\item with \textit{other workers}.
\end{inlinelist}
We'll look at workers' relationships with work itself, which we'll discover
gives us insight into why people engage in crowd work in the first place.

\topic{\ali{some topic sentence that brings together the debate where
one side blames Turkers for being bad at Turking and
another side blames requesters for not understanding Turkers as a culture of people.}}
Early on, \citeauthor{turkopticon} highlighted
the information asymmetry between workers and requesters on AMT,
leading to the creation of \textit{Turkopticon}, a site which allows
Turkers to rate and review requesters
\cite{turkopticon}.
\citeauthor{dynamo} took this critique on information asymmetry and power imbalances a step further,
% pointing out the frustration workers experience trying
designing \textit{Dynamo} to facilitate
Turkers acting collectively to bring about changes to their circumstances
--- this led to the Academic Requester Guidelines
\cite{dynamo}.
\citeauthor{fixingChaos} has since identified the chaos inherent to ``Turking'',
the unbridled power requesters have, and
the distress this causes for workers,
calling for a solution

some research frames this tension as the turker's problem
(see \citeauthor{MaliciousCrowdworkersGadiraju}),
but some has taken a more even--handed view (\citeauthor{takingAHITMcInnis})
\cite{turkopticon,dynamo,MaliciousCrowdworkersGadiraju,takingAHITMcInnis}.

\topic{}
\citeauthor{dynamo} specifically points out the ``mega--drama'' among workers;
\citeauthor{irani2015cultural} and \citeauthor{storiesIraniSilberman} discuss
the culture of crowd work and the study thereof.
\citeauthor{crowdcollab} quantifies and maps this social network of turkers
(this is different from the requesters topic because
researchers like Irani, Gray, etc\dots~aren't Turkers, but are as close to
``cultural anthropologists doing ethnography'' as we see on AMT, maybe online in general)
\cite{dynamo,irani2015cultural,storiesIraniSilberman,crowdcollab}.
% \end{enumerate}

\subsubsubsection{\pieceworkpers}
% \begin{enumerate}
  how do workers relate to work?
  %       \citeauthor{riisOtherSideLives} documents this to some extent,
  %       but doesn't say that much about interviews or anything like that.
  %       a handful of sources suggest to know something about
  %       how workers relate to the work, like \citeauthor{clark1908cotton},
  %       but this distinctly doesn't bring the worker's perspective into the discussion;
  %       it projects an etic view, rather than attempts to understand from an emic view.
  %       then again, this was a time before Boas and Malinowski, so maybe this is natural.
  %       \cite{riisOtherSideLives,clark1908cotton}.
  % \item
          The primary avenue for workers to interact with requesters or managers has been through
        laborer advocacy groups, which later became guilds, unions, etc\dots
        and through that lens, there's a lot of research on
        the relationships between workers and requesters
        \cite{levi2009union,ahlquist2013interest,
              mccallum2013global,jacoby1983union}.
        One component of collectively negotiating with managers has been the process
        of collective action, a topic which has been substantively explored
        but is not quite yet answered
        \cite{russell1982collective,olsonlogic}.
  % \item
  this is harder; crowd work research doesn't just benefit from
        digitally mediated technology allowing us to make
        relationship networks like \citeauthor{crowdcollab} did;
        we also benefit from what we consider modern Anthropology and ethnography,
        something which fundamentally didn't exist or was still in its infancy during piecework's life.
        Still, we can look at primary sources, like \cite{american1921problem} by
        the president of the American Federation of Labor,
        to give us some hint of how they related to each other
        \cite{american1921problem,crowdcollab}.
% \end{enumerate}

@@

While the historical management of workers had to be done by hiring a foreman,
who necessarily had an intuitive
--- perhaps sympathetic ---
relationship with workers,
the foreman of the \nth{20} century has largely been replaced
by the algorithm of the \nth{21} century
\cite{uberAlgorithm}.
The result of this change is that the agents managing work are now
cold and logical, if unforgiving.
Where a person might recognize that the ``attention check'' questions 
proposed by \citeauthor{le2010ensuring} ensure that malicious and inattentive are stopped,
some implementations of these approaches
(\cite[see][]{MaliciousCrowdworkersGadiraju}
only seem to antagonize workers
\cite{le2010ensuring,MaliciousCrowdworkersGadiraju}

\subsubsubsection{\implication}

>>>>

\subsubsubsection{\crowdworkpers}
\topic{The relationships of workers
% with their work,
with their peers and
with requesters
are nuanced and not especially well--understood.}
Researchers have begun to appreciate
the sociality of crowd workers in labor markets;
still, the study of these communities is made more challenging by
the limited access to workers on these sites of work
inherent to digital spaces made without social affordances
\cite{crowdcollab,miller2011understanding}.
We can break this general body of work into two subgroups:
workers' relationships
\begin{inlinelist}
% \item with \textit{work}, % \nameref{ch:workRelationship},
\item with \textit{requesters}, and
\item with \textit{other workers}.
\end{inlinelist}
We'll look at workers' relationships with work itself, which we'll discover
gives us insight into why people engage in crowd work in the first place.

\topic{\ali{some topic sentence that brings together the debate where
one side blames Turkers for being bad at Turking and
another side blames requesters for not understanding Turkers as a culture of people.}}
Some research frames this tension as the Turker's problem
(see, for example, \citeauthor{MaliciousCrowdworkersGadiraju}'s work,
which frames the problem of unpredictable work as the result of ``malicious'' crowd workers),
\cite{MaliciousCrowdworkersGadiraju,Sheng:2008:GLI:1401890.1401965,Ipeirotis:2010:QMA:1837885.1837906}.

Early on, \citeauthor{turkopticon} highlighted
the information asymmetry between workers and requesters on AMT,
leading to the creation of \textit{Turkopticon}, a site which allows
Turkers to rate and review requesters
\cite{turkopticon}.
\citeauthor{dynamo} took this critique on information asymmetry and power imbalances a step further,
designing \textit{Dynamo} to facilitate
Turkers acting collectively to bring about changes to their circumstances
--- this led to the Academic Requester Guidelines
\cite{dynamo}.
This unbridled power that requesters have over workers and
the resultant stress and frustration that this generates
has been part of the undercurrent of research into
the tense relationships between workers and requesters
\cite{fixingChaos,dynamo}.

\topic{The frustration that workers experience dealing with requesters
seems to precipitate frustration and mistrust between crowd workers, as well.}
\citeauthor{dynamo} describes ``mega--drama'' among workers on forums for Turkers;
\citeauthor{irani2015cultural} and \citeauthor{storiesIraniSilberman} discuss
the culture of crowd work and the study thereof.
\citeauthor{crowdcollab} quantifies and maps this social network of Turkers.
\citeauthor{takingAHITMcInnis} takes these observations and considers
what a crowd work platform might look like if it were to be designed more inclusively
\cite{dynamo,irani2015cultural,storiesIraniSilberman,crowdcollab,takingAHITMcInnis}.
The overarching theme of the research in this space has been
documenting the struggle of crowd workers
and attempting to intervene in constructive ways, while walking the balancing act
(especially in the cases of \citeauthor{irani2015cultural} and later \citeauthor{storiesIraniSilberman})
as we think about the culture of crowd workers.

\subsubsubsection{\pieceworkpers}
\topic{The questions surrounding
the ways pieceworkers related to managers might be best answered by
the work that has been done in the emergence and proliferation of labor unions.}
The primary avenue for workers to interact with managers has been through
laborer advocacy groups such as the American Federation of Labor,
(one of the forerunners of the largest and
most politically influential labor union in the United States).
Looking through that lens, we find copious research on
the relationships between workers and requesters
\cite{levi2009union,ahlquist2013interest,
      mccallum2013global,jacoby1983union}.
One component of collectively negotiating with managers has been the process
of collective action, a topic which has been substantively explored
but is not quite yet answered
\cite{russell1982collective,olsonlogic}.

\topic{Answering how workers related to one another is arguably more challenging
for a number of reasons.}
For one thing, the research methods we typically associate with the exploratory study of cultures
--- Anthropology, and namely participant--observation, ethnography, etc\dots ---
didn't exist quite as we know them at the turn of the \nth{20} century, and
wouldn't for several more decades.
Still, we can look at primary sources, like \citetitle{american1921problem}
to give us some hint of how they related to each other
\cite{american1921problem}.

\ali{What do I want to do/say here? I think I want to point to point out that
\dots~I dunno. I'll review the \citetitle{american1921problem} book and maybe some other stuff}

@@

While the historical management of workers had to be done by hiring a foreman,
who necessarily had an intuitive
--- perhaps sympathetic ---
relationship with workers,
the foreman of the \nth{20} century has largely been replaced
by the algorithm of the \nth{21} century
\cite{uberAlgorithm}.
The result of this change is that the agents managing work are now
cold and logical, if unforgiving.
Where a person might recognize that the ``attention check'' questions 
proposed by \citeauthor{le2010ensuring} ensure that malicious and inattentive are stopped,
some implementations of these approaches
(\cite[see][]{MaliciousCrowdworkersGadiraju}
only seem to antagonize workers
\cite{le2010ensuring,MaliciousCrowdworkersGadiraju}.

\subsubsubsection{\implication}
\topic{What we've done in the field of crowd work might be able to tell us something about piecework
just as piecework has told us so much about crowd work.}
Crowd work research doesn't just benefit from
digital media allowing us to make
relationship networks like \citeauthor{crowdcollab} do;
we benefit from the firmer theoretical basis of Anthropology that
existed in a radically different form at the turn of the \nth{20} century,
when piecework began to emerge.
\citeauthor{malinowski2002argonauts,boas1940race,mead1973coming} and
other luminaries throughout the first half of the \nth{20} century
effectively defined Cultural Anthropology as we know it today;
\textit{participant--observation},
the \textit{etic} and the \textit{emic} understanding of culture, and
\textit{reflexivity}
didn't take even a resemblance of their contemporary forms until these works
\cite{malinowski2002argonauts,boas1940race,mead1973coming}.
